### 2015-07-06 narrative/intro.tex
Polishing intro

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time to knowledge'' from 
scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

Avoiding impending bottlenecks in exascale scientific discovery will require
new research into managing and storing the large amounts of data that will be
produced by simulations and analyzed for months afterwards.
%
In this project we will demonstrate a cooperative approach for storing data
where the user and the storage system work together to achieve the best
possible utility and performance given data features, storage tier
characteristics, and current system state. We will investigate novel techniques
to facilitate efficient mapping of data objects, even partitioning individual
variables, from the user space onto multiple storage tiers and enable
application-guided data reductions/transformations to address capacity and
bandwidth bottlenecks, while constraining errors to be within user provided
bounds.
%

>>>>

{\em The purpose of computing is insight, not numbers}~\cite{Hamming:book}.
Richard Hamming's remark, made over 50 years ago at the dawning of the age of
large scale scientific computation, is even more relevant today as we prepare
for scientific simulation at exascale. 
The central objective of this proposal, ``minimizing the time to knowledge''  
with respect to scientific computing, aligns perfectly with this sentiment. 
%Hamming was a pioneer in the fields of coding theory, scientific computing and 
%information theory who would instantly sympathize with the central objective of 
%this proposal--minimizing the time to knowledge.

As we move forward, avoiding impending bottlenecks in exascale scientific discovery will require
new research into managing and storing the large volumes of data that are 
produced by simulations and analyzed for months afterwards.
%
In this project we will demonstrate a cooperative approach for storing data
where the user and the storage system work together to achieve the best
possible utility and performance given data features, storage tier
characteristics, and current system state. We will investigate novel techniques
to facilitate efficient mapping of data objects
from the user space onto multiple storage tiers and enable
application-guided data reductions/transformations to address capacity and
bandwidth bottlenecks, while constraining errors to be within user provided
bounds.
%
